### 2024-09-17 evaluating-prediction-accuracy.qmd
20240917 - updates

- [discrimination](#sec-discrimination):
  - [adjusted $R^2$](#sec-adjustedRsquared)
- [calibration](#sec-calibration):
  - [calibration plot](#sec-calibrationPlot)
- [general accuracy](#sec-calibration):
  - [RMSE](#sec-rootMeanSquaredError)

If you focus on only one accuracy index, [RMSE](#sec-rootMeanSquaredError) would be a good choice.
However, I would also examine a [calibration plot](#sec-calibrationPlot) to evaluate whether predictions are poorly calibrated at higher levels of points.
I would also examine [ME](#sec-meanError)—not to compare the accuracy of various predictions per se—but to determine whether predictions are systematically under- or overestimating actual points.
If so, predictions may be able to be refined by adding or subtracting a constant to the predictions; however, this could worsen other accuracy indices, so it is important to conduct an iterative process of modifying then evaluating, then further modifiying and evaluating, etc.
It may also be valuable to evaluate the accuracy of various subsets of the predictions.
For instance, you might examine the predictive accuracy of players whose project points are greater than 100, to evaluate the accuracy of predictions specifically to distinguish between players at higher levels of points.

@@

- [discrimination](#sec-discrimination):
  - [area under the receiver operating curve](#sec-auc)
  - and, secondarily—depending on the particulary cutoff and the relative costs of false positives versus false negatives:
    - [sensitivity](#sec-sensitivity)
    - [specificicity](#sec-specificity)
    - [positive predictive value](#sec-ppv)
    - [negative predictive value](#sec-npv)
- [calibration](#sec-calibration):
  - [calibration plot](#sec-calibrationPlot)
  - [Spiegelhalter's *z*](#sec-spiegelhalterZ)
  - [Mean difference between observed and predicted values](#sec-miscalibration)

>>>>

- [discrimination](#sec-discrimination):
  - [adjusted $R^2$](#sec-adjustedRsquared)
- [calibration](#sec-calibration):
  - [calibration plot](#sec-calibrationPlot)
- [general accuracy](#sec-calibration):
  - [MAE](#sec-meanAbsoluteError)
  - [RMSE](#sec-rootMeanSquaredError)

If you focus on only one accuracy index, [MAE](#sec-meanAbsoluteError) or [RMSE](#sec-rootMeanSquaredError) would be a good choice.
However, I would also examine a [calibration plot](#sec-calibrationPlot) to evaluate whether predictions are poorly calibrated at higher levels of points.
I would also examine [ME](#sec-meanError)—not to compare the accuracy of various predictions per se—but to determine whether predictions are systematically under- or overestimating actual points.
If so, predictions may be able to be refined by adding or subtracting a constant to the predictions (or to a subset of the predictions); however, this could worsen other accuracy indices, so it is important to conduct an iterative process of modifying then evaluating, then further modifying and evaluating, etc.
It may also be valuable to evaluate the accuracy of various subsets of the predictions.
For instance, you might examine the predictive accuracy of players whose projected points are greater than 100, to evaluate the accuracy of predictions specifically to distinguish between players at higher levels of points, which is one of the key goals when selecting which players to draft.

@@

- [discrimination](#sec-discrimination):
  - [area under the receiver operating curve](#sec-auc)
  - and, secondarily—depending on the particulary cutoff and the relative costs of [false positives](#sec-falsePositive) versus [false negatives](#sec-falseNegative):
    - [sensitivity](#sec-sensitivity)
    - [specificicity](#sec-specificity)
    - [positive predictive value](#sec-ppv)
    - [negative predictive value](#sec-npv)
- [calibration](#sec-calibration):
  - [calibration plot](#sec-calibrationPlot)
  - [Spiegelhalter's *z*](#sec-spiegelhalterZ)
  - [Mean difference between observed and predicted values](#sec-miscalibration)
